---
title: "Plotting Emojis in R Graphs"
author: "Yixuan Qiu"
date: "12/03/2015"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Plotting Emojis in R Graphs}
output: knitr:::html_vignette
---

<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Plotting Emojis in R Graphs}
-->

## Easy Emoji!

Plotting emojis in R can be as easy as plotting regular text. The idea is to use
the [remoji](https://github.com/richfitz/remoji) package to obtain emoji strings,
and to use the [showtext](https://github.com/yixuan/showtext) package
to draw the symbols. The `fontemoji` package loads the
[OpenSansEmoji](https://github.com/MorbZ/OpenSansEmoji) font
(included in the package) and registers it to the `showtext` database with
the family name "emoji", so that emojis can be plotted using any text drawing
functions in R.

## Base Graphics

Below is a quick example:

```{r message=FALSE, fig.height=7, fig.width=7, fig.showtext=TRUE}
library(showtext)
library(fontemoji)
library(remoji)

showtext.auto()

set.seed(123)
x11()
plot(1, type = "n", xlim = c(0, 12), ylim = c(0, 12),
     xlab = "Days left towards deadline", ylab = "Tasks to do")
text(rnorm(20, 7, 2), rnorm(20, 4, 2), emoji("smile"), col = "red",
     cex = 2, family = "emoji")
text(rnorm(20, 4, 2), rnorm(20, 7, 2), emoji("cry"), col = "steelblue",
     cex = 2, family = "emoji")
```

The names of emoji symbols can be found in the
[Emoji cheat sheet](http://www.emoji-cheat-sheet.com/).

## ggplot2 Graphics

Want some `ggplot2`-flavored plots? The idea is the same:

```{r message=FALSE, fig.height=7, fig.width=9, fig.showtext=TRUE}
library(showtext)
library(fontemoji)
library(remoji)
library(ggplot2)

showtext.auto()

dat = data.frame(x = emoji(c("+1", "-1")), y = c(1000, 100))
x11()
ggplot(dat, aes(x = x, y = y)) +
    geom_bar(aes(fill = x), stat = "identity", width = 0.5) +
    scale_fill_hue("", labels = sub_emoji(c("Good! :satisfied:",
                                            "Oh no... :disappointed:"))) +
    xlab("") + ylab("Votes") + ggtitle("How Do You Like This Package?") +
    theme(axis.text.x = element_text(family = "emoji", size = 30),
          legend.text = element_text(family = "emoji", size = 20),
          legend.key.size = grid::unit(1, "cm"),
          title = element_text(size = 20))
```
